## Editorial Boards

```{r}
#| label: editorial
#| output: asis

tibble::tribble(
  ~Years, ~Role, ~Name,
  "2024--Present", "\\textbf{Editorial Board}", "\\emph{Journal of Motor Behavior}",
  "2022--Present", "\\textbf{Managing Board}", "\\emph{Peer Community in Health \\& Movement Sciences}",
  "2022--Present", "\\textbf{Section Editor (Sensorimotor Control)}", "\\emph{Communications in Kinesiology}",
) |> 
  dplyr::mutate(
    description = paste(Role, "; ", Name, sep = "")
  ) |> 
  dplyr::select(Years, description) |> 
  baretable(align = c('llp{15cm}'))
```


## Grant and Personnel Committees

```{r}
#| label: grants-personnel-committees
#| output: asis

tibble::tribble(
  ~Years, ~Role, ~Name,
  "2019", "\\textbf{Reviewer}", "Canadian Society for Psychomotor Learning \\& Sport Psychology Franklin Henry Young Scientist Award (Motor Control \\& Learning)",
  "2019", "\\textbf{Reviewer}", "Ontario Women's Health Scholarship",
  "2012--13", "\\textbf{Reviewer}", "University of Ottawa Faculty of Health Sciences Research Funding",
) |> 
  dplyr::mutate(
    description = paste(Role, "; ", Name, sep = "")
  ) |> 
  dplyr::select(Years, description) |> 
  baretable(align = c('llp{15cm}'))
```


## Executive Positions

```{r}
#| label: executive-positions
#| output: asis

tibble::tribble(
  ~Years, ~Role, ~Name,
  "2023--Present", "\\textbf{Chair}", "\\emph{Society for Transparency, Openness, and Replication in Kinesiology} (STORK)",
  "2022--23", "\\textbf{Co-Chair}", "\\emph{Society for Transparency, Openness, and Replication in Kinesiology} (STORK)",
) |> 
  dplyr::mutate(
    description = paste(Role, "; ", Name, sep = "")
  ) |> 
  dplyr::select(Years, description) |> 
  baretable(align = c('llp{15cm}'))
```


## Ad hoc Journal Referee

Total number of reviews = 61

\vspace{1em}

- Biological Psychology
- Canadian Journal of Experimental Psychology
- Clinical Neurophysiology
- Communications in Kinesiology
- European Journal of Sport Science
- Experimental Brain Research
- Frontiers in Psychology
- Gait & Posture
- Human Movement Science
- International Review of Sport and Exercise Psychology
- Journal of Learning & Instruction
- Journal of Motor Behavior
- Journal of Neurophysiology
- Journal of Motor Learning & Development
- Journal of Sport Sciences
- Perceptual & Motor Skills
- Psychological Research
- Psychology of Sport & Exercise
- Quarterly Journal of Experimental Psychology
- Research Quarterly for Exercise & Sport
- Sport, Exercise, and Performance Psychology

## External Grant Reviews

```{r}
#| label: external-grant-reviews
#| output: asis

tibble::tribble(
  ~Year, ~Name, ~Program,
  "2022", "\\textbf{NSERC Discovery Grant Program}", "Biological Systems and Functions",
  "2021", "\\textbf{NSERC Discovery Grant Program}", "Biological Systems and Functions",
) |> 
  dplyr::mutate(
    description = paste(Name, ", ", Program, sep = "")
  ) |> 
  dplyr::select(Year, description) |> 
  baretable(align = c('llp{15cm}'))
```

## Volunteer Positions

```{r}
#| label: volunteer
#| output: asis

tibble::tribble(
  ~Years, ~Role, ~Name,
  "2022--Present", "\\textbf{Moderator}", "\\emph{SportR$\\chi$iv} preprint server",
  "2022--Present", "\\textbf{Typesetter}", "\\emph{Communications in Kinesiology}",
) |> 
  dplyr::mutate(
    description = paste(Role, ", ", Name, sep = "")
  ) |> 
  dplyr::select(Years, description) |> 
  baretable(align = c('llp{15cm}'))
```
