$^\dagger$Denotes student won external funding

## Master's

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Program, ~Funding, ~Status,
  "2023--", "Daniel Deletsu$^\\dagger$", "Kinesiology", "Brain Canada, Heart \\& Stroke, CIHR Black Scholars Award", "",
  "2022--", "Nour Al Afif", "Kinesiology", "", "",
  "2022--", "Mikayla Lalli", "Kinesiology", "", "",
  "2019--21", "Mirette Mounir$^\\dagger$", "Kinesiology", "SSHRC CGS-M", "Dentistry school",
  "2019--21", "Rajbir Sidhu$^\\dagger$", "Kinesiology", "NSERC CGS-M", "Dentistry school",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE) |> 
  column_spec(column = 1, width = "1.75cm") |> 
  column_spec(column = 2, width = "3.65cm") |> 
  column_spec(column = 3, width = "2.75cm") |> 
  column_spec(column = 4, width = "4cm") |> 
  column_spec(column = 5, width = "4.5cm")
```


## Doctoral

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Program, ~Funding, ~Status,
  "2023--", "Jiaqiao (Jack) Tang", "Kinesiology", "", "",
  "2018--23", "Laura St. Germain$^\\dagger$", "Kinesiology", "NSERC PGS-D", "Research and Data Specialist at Sheridan College",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE) |> 
  column_spec(column = 1, width = "1.75cm") |> 
  column_spec(column = 2, width = "3.65cm") |> 
  column_spec(column = 3, width = "2.75cm") |> 
  column_spec(column = 4, width = "4cm") |> 
  column_spec(column = 5, width = "4.5cm")
```


## Postdoctoral fellows

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Program, ~Funding, ~Status,
  "2021--23", "Dr. Brad McKay", "Kinesiology", "", "Senior Strategist of Training Design for the Milwaukee Brewers",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE) |> 
  column_spec(column = 1, width = "1.75cm") |> 
  column_spec(column = 2, width = "3.65cm") |> 
  column_spec(column = 3, width = "2.75cm") |> 
  column_spec(column = 4, width = "4cm") |> 
  column_spec(column = 5, width = "4.5cm")
```


## Undergraduates -- Honours thesis

*Denotes student was co-supervised

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Program, ~Course, ~University,
  "2023--", "Lidia Barbera", "Life Sciences", "4C12", "McMaster University",
  "2023--", "Ola Schwarzenberg", "Life Sciences", "4C12", "McMaster University",
  "2023--", "Hibaa Hasan", "Neuroscience", "4D09", "McMaster University",
  "2023--", "Mithun Manivannan", "Kinesiology", "4RR6", "McMaster University",
  "2022--23", "Chitrini Tandon", "Life Sciences", "4C12", "McMaster University",
  "2022--23", "Alyssa Skouros", "Biology", "4C12", "McMaster University",
  "2022--23", "Kiana Masoudi", "Biology", "4C12", "McMaster University",
  "2021--22", "Raika Bourmand", "Kinesiology", "4RR6", "McMaster University",
  "2021--22", "Armin Sariaslani", "Life Sciences", "4C12", "McMaster University",
  "2021--22", "Katharine Douglas", "Life Sciences", "4C12", "McMaster University",
  "2021--22", "Thinzar Soe", "Life Sciences", "4B09", "McMaster University",
  "2020--21", "Julianna Marfisi", "Kinesiology", "4RR6", "McMaster University",
  "2020--21", "Matthew Tobis", "Kinesiology", "4RR6", "McMaster University",
  "2020--21", "Andrew Poskus", "Kinesiology", "4RR6", "McMaster University",
  "2019--20", "Sherry Feldman", "Life Sciences", "4C12", "McMaster University",
  "2019--20", "Olena Leschyshen", "Kinesiology", "4RR6", "McMaster University",
  "2019--20", "Noura Balbaa", "Kinesiology", "4RR6", "McMaster University",
  "2016--17", "Lauren Smail*", "Psychology", "501", "Queen's University",
  "2016--17", "Zachary Yantha*", "Human Kinetics", "4100", "University of Ottawa",
  "2015--16", "Michelle Nguyen*", "Human Kinetics", "4100", "University of Ottawa",
  "2014--15", "Victoria Smith*", "Human Kinetics", "4100", "University of Ottawa",
  "2014--15", "Anna Head*", "Human Kinetics", "4100", "University of Ottawa",
  "2013--14", "Bethany Cseke*", "Human Kinetics", "4100", "University of Ottawa",
  "2013--14", "Dylan Klawitter*", "Human Kinetics", "4100", "University of Ottawa",
  "2013--14", "Codie Primeau*", "Human Kinetics", "4100", "University of Ottawa",
  "2012--13", "Helen Chong*", "Human Kinetics", "4100", "University of Ottawa",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE)
```


## Undergraduates -- Research practicum/project

\vspace{-1em}

```{r}
tibble::tribble(
  ~`Year(s)`, ~Name, ~Program, ~Course, ~University,
  "Winter 2024", "Michael Croteau", "Neuroscience", "3DD3", "McMaster University",
  "Winter 2024", "Francesca Caputo", "Biology", "3IR3", "McMaster University",
  "Winter 2024", "Jil Soni", "Life Sciences", "3RP3", "McMaster University",
  "Winter 2024", "Navishka Brahmbhatt", "Life Sciences", "4A03", "McMaster University",
  "Winter 2024", "Aditya Trivedi", "Life Sciences", "3RP3", "McMaster University",
  "2023--", "Abby Girouard", "Neuroscience", "3DD6", "McMaster University",
  "2023--", "Jacqueline Zhang", "Neuroscience", "3DD6", "McMaster University",
  "Fall 2023", "Enuri Dissanayake", "Life Sciences", "3RP3", "McMaster University",
  "2022--23", "Jeswende Seedu", "Health Sciences", "3H06", "McMaster University",
  "Winter 2022", "Vivian Li", "Mechatronics \\& Biomedical Engineering", "3H03", "McMaster University",
  "Winter 2022", "Caroline Jarvi", "Life Sciences", "3RP3", "McMaster University",
  "Fall 2021", "Gurlal Gill", "Kinesiology", "3RP3", "McMaster University",
  "Fall 2021", "Anita Chaseendran", "Life Sciences", "3RP3", "McMaster University",
  "Fall 2021", "Gianna Jeyarajan", "Life Sciences", "3RP3", "McMaster University",
  "Winter 2021", "Kenzie Bell", "Kinesiology", "3RP3", "McMaster University",
  "Winter 2021", "Ashton Yuen", "Kinesiology", "3RP3", "McMaster University",
  "Winter 2021", "Charlie Violin", "Kinesiology", "3RP3", "McMaster University",
  "Winter 2020", "Ammaar Jan", "Kinesiology", "3RP3", "McMaster University",
  "Winter 2020", "Faran Chaudhry", "Health Sciences", "4D03", "McMaster University",
  "Winter 2020", "Yu (Sarah) Fu", "Health Sciences", "3H03", "McMaster University",
  "Winter 2019", "Maya El-Zahed", "Kinesiology", "3RP3", "McMaster University",
  "Winter 2019", "Grant Yang", "Kinesiology", "3RP3", "McMaster University",
  "Fall 2019", "Andrew Poskus", "Kinesiology", "3RP3", "McMaster University",
  "Fall 2019", "Olena Leshchyshen", "Kinesiology", "3RP3", "McMaster University",
  "Winter 2018", "Rita Waseem", "Life Sciences", "3RP3", "McMaster University",
  "Fall 2018", "Christian Kleiser", "Kinesiology", "3RP3", "McMaster University",
  "Fall 2018", "Christopher Li", "Kinesiology", "3RP3", "McMaster University",
  "Spring 2018", "Faryal Zahir", "Biology", "3RP3", "McMaster University",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE) |> 
  column_spec(column = 3, width = "4.5cm")
```


## Undergraduates -- Research Assistants

\vspace{-1em}

```{r}
tibble::tribble(
  ~`Year(s)`, ~Name, ~Program, ~Type, ~University,
  "2022--", "Vida Sussma", "Psychology", "Volunteer", "McMaster University",
  "2022--23", "Lidia Barbera", "Life Sciences", "Volunteer", "McMaster University",
  "2022--23", "Hibaa Hasan", "Life Sciences", "Volunteer", "McMaster University",
  "2022", "Faith Adams", "Neuroscience", "Volunteer", "McMaster University",
  "2021--", "Celeste De Faveri", "Biomedical Science", "Volunteer", "McGill University",
  "2021--22", "Chitrini Tandon", "Life Sciences", "Volunteer", "McMaster University",
  "2021--22", "Kristen Arnold", "Life Sciences", "Volunteer", "McMaster University",
  "2020--23", "Elizabeth Mitchell", "Integrated Biomedical Engineering \\& Health Sciences", "Co-op / Volunteer", "McMaster University",
  "2018--20", "Allison Williams", "Kinesiology", "Volunteer / NSERC USRA", "McMaster University",
  "2019", "Andrew Poskus", "Kinesiology", "NSERC USRA", "McMaster University",
  "2019", "Sherry Feldman", "Life Sciences", "Volunteer", "McMaster University",
  "2019", "Kevin Gilotra", "Kinesiology", "Volunteer", "McMaster University",
  "2019", "Ashton Yuen", "Kinesiology", "Volunteer", "McMaster University",
  "2019--21", "Kenzie Bell", "Kinesiology", "Volunteer", "McMaster University",
  "2018--19", "Olena Leshchyshen", "Kinesiology", "Volunteer", "McMaster University",
  "2018--19", "Yu (Sarah) Fu", "Health Sciences", "Volunteer", "McMaster University",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE) |> 
  column_spec(column = 3, width = "4.5cm") |> 
  column_spec(column = 4, width = "3cm")
```


## Advisory committees

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Degree, ~Program, ~University,
  "2021--", "Seth Sullivan", "Ph.D.", "Biomedical Engineering", "University of Delaware",
  "2021--23", "Mary-Anne Vinh", "M.Sc.", "Human Kinetics", "University of Ottawa",
  "2020--", "Adam Roth", "Ph.D", "Mechanical Engineering", "University of Delaware",
  "2020--22", "Karishma Ramdeo", "M.Sc.", "Kinesiology", "McMaster University",
  "2019--", "Stephen Toepp", "Ph.D", "Kinesiology", "McMaster University",
  "2019--21", "Kristen DeMelo", "M.Sc.", "Kinesiology", "McMaster University",
  "2019--21", "Noah Erskine", "M.Sc.", "Kinesiology", "McMaster University",
  "2018--", "Chantal Carillo", "Ph.D", "Psychology", "McMaster University",
  "2018--", "Claire Tuckey", "Ph.D", "Kinesiology", "McMaster University",
  "2018--21", "Patrick Dans", "M.Sc.", "Kinesiology", "McMaster University",
  "2018--20", "Ashley Flemington", "M.Sc.", "Kinesiology", "McMaster University",
  "2018--20", "Jacqueline Brillantes", "M.Sc.", "Kinesiology", "McMaster University",
  "2017--19", "Mitchell Locke", "M.Sc.", "Kinesiology", "McMaster University",
  "2017--19", "Stephen Toepp", "M.Sc.", "Kinesiology", "McMaster University",
  "2017--19", "Stevie Foglia", "M.Sc.", "Kinesiology", "McMaster University",
  "2017--19", "Kumara Somasundram", "M.Sc.", "Kinesiology", "McMaster University",
  "2017--19", "Jessica Cappelletto", "Ph.D", "Kinesiology", "McMaster University",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE)
```


## Thesis examiner

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Degree, ~Program, ~University, ~Role,
  "2023", "Mary-Anne Vinh", "M.Sc.", "Human Kinetics", "University of Ottawa", "External",
  "2018", "Stephaie Reischel", "M.Sc.", "Kinesiology", "Brock University", "External",
  "2018", "Denver Brown", "Ph.D", "Kinesiology", "McMaster University", "Internal",
  "2018", "Jenin El-Sayes", "M.Sc.", "Kinesiology", "McMaster University", "External",
  "2018", "Lana Pfaff", "M.Sc.", "Kinesiology", "Laurier University", "External",
  "2017", "Claire Tuckey", "M.Sc.", "Kinesiology", "Brock University", "External",
  "2017", "Hunter Fassett", "M.Sc.", "Kinesiology", "McMaster University", "External",
) |> 
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE)
```


## Comprehensive examinations

\vspace{-1em}

```{r}
tibble::tribble(
  ~Years, ~Name, ~Degree, ~Program, ~University,
  "2020", "Chantal Carrillo", "Ph.D", "Psychology", "McMaster University",
  "2019", "Claudia Turco", "Ph.D", "Kinesiology", "McMaster University",
) |>
  kbl(
    format = "latex",
    booktabs = TRUE,
    align = "l",
    escape = FALSE,
    longtable = TRUE,
    linesep = ""
  ) |>
  kable_styling(
    position = "left",
    latex_options = c("hold_position", "repeat_header")
  ) |> 
  row_spec(row = 0, bold = TRUE)
```
